MINOS Handover Plots

### 2023-06-16 minos/validation/handovers.Rmd
adding ridge plots into handovers notebook and tweaking arc4 script for all interventions

require(tidyverse)
require(ggplot2)

@@

save.path <- '/Users/robertclay/minos/plots/andovers/'
```

@@

spaghetti_plot(income.spag, 'hh_income',
               save = TRUE,
               save.path = save.path)

@@

@@

## Housing Quality

```{r}
raw.housing <- raw.dat %>% 
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  dplyr::select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
housing <- rbind(raw.housing, base.housing)
housing$housing_quality <- as.factor(housing$housing_quality)

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

housing.norm <- housing %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Housing Quality') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'housing_quality.png',
       plot = last_plot(),
       path = save.path)

rm(raw.housing, base.housing, housing, housing.norm)
```

## Neighbourhood Safety

```{r}
raw.neighbour <- raw.dat %>% 
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  dplyr::select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
neighbour <- rbind(raw.neighbour, base.neighbour)
neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') +
  xlab('Year') +
  ylab('Count')

neighbour.norm <- neighbour %>%
  group_by(time) %>%
  filter(neighbourhood_safety != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Neighbourhood Safety') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'neighbourhood_safety.png',
       plot = last_plot(),
       path = save.path)

#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
```

## Loneliness

```{r}
raw.loneliness <- raw.dat %>% 
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  dplyr::select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')

# merge before plot
loneliness <- rbind(raw.loneliness, base.loneliness)
loneliness$loneliness <- as.factor(loneliness$loneliness)

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness', subtitle = 'Counts by level') +
  xlab('Year') +
  ylab('Count')

loneliness.norm <- loneliness %>%
  group_by(time) %>%
  filter(loneliness != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Loneliness') +
  xlab('Year') +
  ylab('Proportion')

ggsave(filename = 'loneliness.png',
       plot = last_plot(),
       path = save.path)

rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
```

## Nutrition Quality

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  dplyr::select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut <- base.dat %>%
  dplyr::select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
nutrition_quality <- rbind(raw.nut, base.nut)

# Now plot
ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Nutrition Quality', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Nutrition Quality')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.nut2 <- raw.dat %>% 
  dplyr::select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut2 <- base.dat %>%
  dplyr::select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

nutrition_quality2 <- rbind(raw.nut2, base.nut2)

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Nutrition Quality') +
  xlab('Year') +
  ylab('Nutrition Quality')

ggsave(filename = 'nutrition_quality_wav1.png',
       plot = last_plot(),
       path = save.path)

rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
    nutrition_quality2)
```

## Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
phealth <- rbind(raw.phealth, base.phealth)

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.phealth2 <- raw.dat %>% 
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  dplyr::select(pidp, time, phealth) %>%
  filter(time > 2009) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

phealth2 <- rbind(raw.phealth2, base.phealth2)

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Physical Health') +
  xlab('Year') +
  ylab('Average')

ggsave(filename = 'physical_health_wav1.png',
       plot = last_plot(),
       path = save.path)

#raw.phealth.check <- raw.dat %>% 
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

#base.phealth.check <- base.dat %>%
#  select(pidp, time, phealth) %>%
#  filter(time > 2009) %>%
#  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2)
#rm(raw.phealth.check, base.phealth.check)
```

```{r}

```

>>>>

require(tidyverse)
require(ggplot2)
require(ggridges)

@@

save.path <- '/Users/robertclay/minos/plots/handovers/'
```

@@

spaghetti_plot(income.spag, 'hh_income',
               save = TRUE,
               save.path = save.path)
density_ridges(income.spag, 'hh_income',
               save=TRUE, 
               save.path=save.path)

@@

density_ridges(sf12.spag, "SF_12", 
               save = T, 
               save.path = save.path)

@@

<!-- ## Housing Quality -->

<!-- ```{r} -->
<!-- raw.housing <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, housing_quality) %>% -->
<!--   group_by(time, housing_quality) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.housing <- base.dat %>% -->
<!--   dplyr::select(pidp, time, housing_quality) %>% -->
<!--   group_by(time, housing_quality) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- housing <- rbind(raw.housing, base.housing) -->
<!-- housing$housing_quality <- as.factor(housing$housing_quality) -->

<!-- # Now plot -->
<!-- ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Quality', subtitle = 'Counts by Level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- housing.norm <- housing %>% -->
<!--   group_by(time) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Housing Quality') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- ggsave(filename = 'housing_quality.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->

<!-- rm(raw.housing, base.housing, housing, housing.norm) -->
<!-- ``` -->

<!-- ## Neighbourhood Safety -->

<!-- ```{r} -->
<!-- raw.neighbour <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
<!--   group_by(time, neighbourhood_safety) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.neighbour <- base.dat %>% -->
<!--   dplyr::select(pidp, time, neighbourhood_safety) %>% -->
<!--   group_by(time, neighbourhood_safety) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- neighbour <- rbind(raw.neighbour, base.neighbour) -->
<!-- neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety) -->

<!-- # Now plot -->
<!-- ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Neighbourhood Safety', subtitle = 'Counts by level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- neighbour.norm <- neighbour %>% -->
<!--   group_by(time) %>% -->
<!--   filter(neighbourhood_safety != -9) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Neighbourhood Safety') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- ggsave(filename = 'neighbourhood_safety.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->

<!-- #rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm) -->
<!-- ``` -->

<!-- ## Loneliness -->

<!-- ```{r} -->
<!-- raw.loneliness <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, loneliness) %>% -->
<!--   group_by(time, loneliness) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.loneliness <- base.dat %>% -->
<!--   dplyr::select(pidp, time, loneliness) %>% -->
<!--   group_by(time, loneliness) %>% -->
<!--   count() %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- loneliness <- rbind(raw.loneliness, base.loneliness) -->
<!-- loneliness$loneliness <- as.factor(loneliness$loneliness) -->

<!-- # Now plot -->
<!-- ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Loneliness', subtitle = 'Counts by level') + -->
<!--   xlab('Year') + -->
<!--   ylab('Count') -->

<!-- loneliness.norm <- loneliness %>% -->
<!--   group_by(time) %>% -->
<!--   filter(loneliness != -9) %>% -->
<!--   mutate(total = sum(n)) %>% -->
<!--   mutate(prct = (n / total)) -->

<!-- ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) + -->
<!--   geom_bar(stat = 'identity') + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Loneliness') + -->
<!--   xlab('Year') + -->
<!--   ylab('Proportion') -->

<!-- ggsave(filename = 'loneliness.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->

<!-- rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm) -->
<!-- ``` -->

<!-- ## Nutrition Quality -->

<!-- TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11 -->

<!-- ```{r} -->
<!-- # first figure out how to plot final_US -->
<!-- # start with hh_income -->
<!-- raw.nut <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.nut <- base.dat %>% -->
<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- nutrition_quality <- rbind(raw.nut, base.nut) -->

<!-- # Now plot -->
<!-- ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Nutrition Quality', subtitle = 'Full Sample') + -->
<!--   xlab('Year') + -->
<!--   ylab('Nutrition Quality') -->

<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
<!-- # onwards because the sample refreshments are messing with the plot -->
<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->

<!-- raw.nut2 <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   filter(nutrition_quality >= 0) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.nut2 <- base.dat %>% -->
<!--   dplyr::select(pidp, time, nutrition_quality) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- nutrition_quality2 <- rbind(raw.nut2, base.nut2) -->

<!-- # Now plot -->
<!-- ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Nutrition Quality') + -->
<!--   xlab('Year') + -->
<!--   ylab('Nutrition Quality') -->

<!-- ggsave(filename = 'nutrition_quality_wav1.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->

<!-- rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, -->
<!--     nutrition_quality2) -->
<!-- ``` -->

<!-- ## Physical Health -->

<!-- NOTE: At present, physical health is not predicted or transitioned. -->

<!-- ```{r} -->
<!-- # first figure out how to plot final_US -->
<!-- # start with hh_income -->
<!-- raw.phealth <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.phealth <- base.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- # merge before plot -->
<!-- phealth <- rbind(raw.phealth, base.phealth) -->

<!-- # Now plot -->
<!-- ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Physical Health', subtitle = 'Full Sample') + -->
<!--   xlab('Year') + -->
<!--   ylab('Average') -->

<!-- ## Try a version where final_US is limited to only those present from wave 1 -->
<!-- # onwards because the sample refreshments are messing with the plot -->
<!-- raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009] -->

<!-- raw.phealth2 <- raw.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'final_US') -->

<!-- base.phealth2 <- base.dat %>% -->
<!--   dplyr::select(pidp, time, phealth) %>% -->
<!--   filter(time > 2009) %>% -->
<!--   filter(pidp %in% raw.wave1) %>% -->
<!--   group_by(time) %>% -->
<!--   summarise(phealth = mean(phealth, na.rm = TRUE)) %>% -->
<!--   mutate(source = 'baseline_output') -->

<!-- phealth2 <- rbind(raw.phealth2, base.phealth2) -->

<!-- # Now plot -->
<!-- ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) + -->
<!--   geom_line() + -->
<!--   geom_vline(xintercept=start.year, linetype='dotted') + -->
<!--   labs(title = 'Physical Health') + -->
<!--   xlab('Year') + -->
<!--   ylab('Average') -->

<!-- ggsave(filename = 'physical_health_wav1.png', -->
<!--        plot = last_plot(), -->
<!--        path = save.path) -->

<!-- #raw.phealth.check <- raw.dat %>% -->
<!-- #  select(pidp, time, phealth) %>% -->
<!-- #  filter(time > 2009) %>% -->
<!-- #  filter(pidp %in% raw.wave1) -->

<!-- #base.phealth.check <- base.dat %>% -->
<!-- #  select(pidp, time, phealth) %>% -->
<!-- #  filter(time > 2009) %>% -->
<!-- #  filter(pidp %in% raw.wave1) -->

<!-- rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, phealth2) -->
<!-- #rm(raw.phealth.check, base.phealth.check) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- ``` -->
